Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-12-22 journal paper/content/sec-intro.tex
Minor edit.

%We investigate these questions with
\xhdr{Our model: competition game.} We consider a stylized duopoly model in which two firms (\emph{principals}) compete for users (\emph{agents}). Principals compete on quality rather than on prices, and engage in exploration in order to learn which actions lead to high quality products. A new agent arrives and chooses a principal according to some decision rule (which may depend on the principal's exploration strategy, either directly or indirectly). The principal selects an action which affects the quality of service provided to this agent (\eg a list of web search results). The agent experiences this action and the resulting reward from this action is observed by the principal. Each principal only observes its own users. Principals commit to their strategies in advance, so as to maximize their market share.

@@

\textbf{(ii)} We dilute the \HardMax agents with a small fraction of ``random agents" who choose a principal uniformly at random.
(They can be interpreted as consumers that are oblivious to the principals' reputation.) We call this model \HardMaxRandom. Then better algorithms help in a big way: a sufficiently better algorithm is guaranteed to win all non-random agents after an initial learning phase. There is a caveat, however: any algorithm can be defeated by interleaving it with the greedy algorithm. This has two undesirable consequences: a better algorithm may sometimes lose in competition, and a Nash equilibrium typically does not exist.

>>>>

%We investigate these questions with
\xhdr{Our model: competition game.} We consider a stylized duopoly model in which two firms (\emph{principals}) compete for users (\emph{agents}). Principals compete on quality rather than on prices, and engage in exploration in order to learn which actions lead to high quality products. A new agent arrives and chooses a principal according to some decision rule (which may depend on the principal's exploration strategy, either directly or indirectly). The principal selects an action which affects the quality of service provided to this agent, \eg a list of web search results. The agent experiences this action and the resulting reward from this action is observed by the principal. Each principal only observes its own users. Principals commit to their strategies in advance, so as to maximize their market share.

@@

\textbf{(ii)} We dilute the \HardMax agents with a small fraction of ``random agents" who choose a principal uniformly at random.
(They can be interpreted as consumers that are oblivious to the principals' reputation.) We call this model \HardMaxRandom. Then better algorithms help in a big way: \asedit{when two algorithms compete against one another,} a sufficiently better algorithm is guaranteed to win all non-random agents after an initial learning phase. There is a caveat, however: any algorithm can be defeated by interleaving it with the greedy algorithm. This has two undesirable consequences: a better algorithm may sometimes lose in competition, and a Nash equilibrium typically does not exist.
